State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-08 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
periodic commit. added more to discussion. still need to discuss results more

@@

The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model that is capable of capturing the dominant cortical dynamics. These tools can be also used to better design electrophysiological recording techniques to advance model-based neural parameter estimation in order to avoid spatial aliasing. The effect of the basis function decomposition will restrict the frequency content of the estimated field. This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT}. Since the frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel some information will be lost due the decomposition. The implication of this loss of information is the high spatial frequency content of the connectivity kernel. This is demonstrated in Figure~\ref{fig:KernelEstimates} of the results where the frequency content of the estimated connectivity kernel is less than the true kernel.

>>>>

	$\boldsymbol{\theta}$ & $\left[\begin{array}{ccc}
	10 &-8 &0.5
	\right]^{\top}$ & synaptic strength\\
	$\sigma_{\psi,1}$ & 1.8 & inner connectivity kernel width\\
	$\sigma_{\psi,2}$ & 2.4 & middle connectivity kernel width\\
	$\sigma_{\psi,3}$ & 6 & outer connectivity kernel width\\

@@

The frequency analysis and model selection tools presented in this paper specify the sensor and field basis function arrangement required to form a state-space model that is capable of capturing the dominant cortical dynamics. These tools can be also used to better design electrophysiological recording techniques to advance model-based neural parameter estimation in order to avoid spatial aliasing. The effect of the basis function decomposition will restrict the frequency content of the estimated field. This is evident in when comparing Figures~\ref{fig:FieldFFT} and~\ref{fig:EstimatedFieldFFT} where the estimated field field is spatially band-limited. The frequency content of the field is governed by disturbance covariance and the shape of the connectivity kernel, therefore some information will be lost due to the field decomposition. The implication of this loss of information is the high spatial frequency content of the connectivity kernel. This is demonstrated in Figure~\ref{fig:KernelEstimates} of the results where the frequency content of the estimated connectivity kernel is less than the true kernel.
